### 2017-09-22 Sections/protocols_for_the_quantum_internet.tex
indexing

Perhaps the most useful, and ubiquitous, type of optical state measurement is photo-detection \cite{RohdePDReview}, where we would like to count photon-number. Broadly, there are two main classes of photo-detectors -- \textit{number-resolved} and \textit{non-number-resolved} (or `bucket' detectors). These behave exactly as the names suggest, with the former typically being more expensive and technologically demanding than the latter.

@@

Mathematically, the measurement operators for number-resolved detection are,
\begin{align}\index{Number-resolved photo-detection}
\hat\Pi_n = \eta^{n} \sum_{m=n}^\infty \binom{m}{n} (1-\eta)^{m-n} \ket{m}\bra{m},
\end{align}
for measurement outcome $n$, in the photon-number basis. And for non-number-resolved detection,
\begin{align}\index{Non-number-resolved photo-detection}
&\hat\Pi_0 = \sum_{m=0}^\infty (1-\eta)^{m} \ket{m}\bra{m}, \nonumber \\
&\hat\Pi_{>0} = \mathbb{\hat{I}} - \hat\Pi_0.
\end{align}
Thus, inefficiency results in projection onto the wrong photon-number, making measurement outcomes incorrect.

@@

\subsubsection{Quantum non-demolition measurement (QND)}\index{Quantum non-demolition measurement}

@@

Quantum key distribution (QKD) is a relatively mature technology with already several commercial systems being available off-the-shelf. The main drawback is thus the ability to perform long-distance transmission of photons. For these reasons, current QKD networks have been limited to relatively small distances, on the order of $\sim100$km, including in Austria, Switzerland, Japan, USA, and China \cite{bib:lo2014secure}. The longest distance QKD network that is currently planned is the Beijing to Shanghai QKD link spanning a distance of 2000km. This involves 32 trusted nodes\index{Trusted node} to break the total distance into shorter segments to convert the quantum information to classical information.

Utilizing space communications for the purpose of QKD has been discussed in several works \cite{bib:hughes2000quantum, bib:rarity2002ground, bib:pfennigbauer2003free, bib:aspelmeyer2003long, bib:armengol08}. As already demonstrated in space-based entanglement experiments \cite{bib:yin2017satellite, bib:ren2017ground, bib:liao2017satellite} far lower attenuation rates are possible than ground-only approaches. Since cryptography schemes such as BB84\index{BB84} do not require entanglement, these would appear to be the first widespread commercial application for quantum technologies.

The ready realisability of space based QKD was already noted in a variety of configurations including ground-to-space\index{Ground-to-space} and space-to-ground\index{Space-to-ground} quantum communication \cite{bib:rarity2002ground, bib:aspelmeyer2003long}. In the context of security, the first long-distance experiments that are likely to be demonstrated will employ trusted nodes\index{Trusted nodes}. For example, after performing QKD between satellite\index{Satellites} and ground stations, a satellite could store the key for some time until another QKD can be performed to another ground station\index{Ground stations} using a one-time pad\index{One-time-pad cipher} \cite{bib:liao2017satellite}. These types of experiments are planned to eventually perform intercontinental QKD\index{Intercontinental QKD} between China and Austria.

%
% One-Time Pad
%

\paragraph{One-time pad}\index{One-time pad}

@@

We now turn our attention to the technical implementation of QKD and its perfect security. There is only a single provably secure encryption protocol -- the \textit{one-time-pad}\index{One-time pad cipher} \cite{bib:Schneier96}. This protocol requires Alice and Bob to share a random bit-string as long as the message (plaintext\index{Plaintext}) being communicated between them. The two bit-strings undergo bit-wise XOR operations to form the ciphertext\index{Ciphertext}. Mathematically,\index{One-time-pad cipher}
\begin{align}
c = s \oplus k,
\end{align}
where $\oplus$ is the bitwise XOR operation (equivalently addition modulo 2), and $c$, $s$ and $k$ are the ciphertext, plaintext and key strings respectively, all of which are of the same length, \mbox{$|c|=|s|=|k|$}.

@@

Importantly, the secrecy of the one-time-pad\index{One-time-pad} strictly requires that a key never be reused. A fresh key must be generated for each message sent, otherwise trivial frequency analysis\index{Frequency analysis} techniques can be employed to compromise security\footnote{If the same key $k$ is used to encode two messages $s_1$ and $s_2$, yielding ciphertexts \mbox{$c_1=s_1\oplus k$} and \mbox{$c_2=s_2\oplus k$}, then we trivially obtain \mbox{$c_1 \oplus c_2 = s_1 \oplus k \oplus s_2 \oplus k = s_1 \oplus s_2$}. Now a frequency analysis on the bitwise XOR of two plaintexts can be applied, without requiring any knowledge of the key whatsoever.}.

Needless to say, the requirement for keys of the same length as the plaintexts, which cannot be reused, raises the obvious criticism that now secret key-sharing is as difficult as sharing a secret message in the first place. This reduces the problem of perfect secrecy of arbitrary messages to the secrecy of shared randomness. QKD protocols enable this by providing a shared source of randomness between Alice and Bob, where any intercept-resend attack\index{Intercept-resend attack} (man-in-the-middle attack\index{Man-in-the-middle attack})\index{Man-in-the-middle attack} may be detected, guaranteed by the laws of quantum physics (specifically the Heisenberg uncertainty principle\index{Heisenberg uncertainty principle} and no-cloning theorem\index{No-cloning theorem}).

@@

The two original QKD protocols, known as the \textit{BB84} \cite{bib:BennetBrassard84}\index{BB84 QKD protocol}, and \textit{E91} \cite{bib:Ekert91}\index{E91 QKD protocol} protocols, are based on polarisation encoding in photons. BB84 requires only the transmission of a sequence of single photons, polarisation-encoded\index{Polarisation encoding} with random data. E91, on the other hand, requires a server that distributes entangled Bell-pairs between Alice and Bob. Since then, numerous other protocols for QKD have been proposed, for example, using CV (ontinuous variable) states\index{Continuous variable QKD}.

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function BB84():
\begin{enumerate}
\item Alice chooses a random bit $0$ or $1$.
\item Alice randomly chooses a basis, $\hat{X}$ or $\hat{Z}$.
\item Depending on the choice of basis, she encodes her bit into the polarisation of a single photon as:
\begin{align}
\ket{0}_Z &\equiv \ket{H}, \nonumber \\
\ket{1}_Z &\equiv \ket{V},
\end{align}
or,
\begin{align}
\ket{0}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}+\ket{V}), \nonumber \\
\ket{1}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}-\ket{V}).
\end{align}
\item Encoding into the randomly chosen basis, she transmits the randomly chosen bit to Bob.
\item She does not announce the choice of bit or basis.
\item Bob measures the bit in a randomly chosen basis, $\hat{X}$ or $\hat{Z}$.
\item The above is repeated many times.
\item Upon receipt of all qubits, Alice (publicly) announces the basis used for encoding each bit sent.
\item Qubits where Bob measured in the opposite basis to which Alice encoded are discarded, as they will be decorrelated from Alice.
\item The remaining measurement outcomes are guaranteed to yield identical bits between Alice and Bob.
\item Remaining is roughly half as many bits as were sent, which are random, but guaranteed to be identical between Alice and Bob.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\end{enumerate}}}}
\caption{BB84 QKD protocol using polarisation-encoded\index{Polarisation encoding} photons. Upon completion of the protocol, Alice and Bob share a random bit-string. Suppose an eavesdropper, Eve, were to perform an intercept-resend\index{Intercept-resent attack} attack on the channel between Alice and Bob. At that stage in the protocol Alice had not yet announced her choice of bases, and Eve will not know the bases in which to measure states without randomly collapsing them onto values inconsistent with Alice's encoding. By sacrificing a some of their shared bits, via openly communicating them to one another for comparison, such an attack will be detected with asymptotically high security. Thus, Alice and Bob have great confidence that they have a shared, secret, random bit-string, which may subsequently be employed in a one-time-pad.\index{One-time-pad}}\label{alg:bb84}
\end{table}

@@

>>>>

Perhaps the most useful, and ubiquitous, type of optical state measurement is photo-detection \cite{bib:RohdePDReview}, where we would like to count photon-number. Broadly, there are two main classes of photo-detectors -- \textit{number-resolved}\index{Number-resolved photo-detectors} and \textit{non-number-resolved}\index{Non-number-resolved photo-detectors} (or `bucket' detectors). These behave exactly as the names suggest, with the former typically being more expensive and technologically demanding than the latter.

@@

Mathematically, the measurement operators for number-resolved detection are,
\begin{align}\index{Number-resolved photo-detectors}
\hat\Pi_n = \eta^{n} \sum_{m=n}^\infty \binom{m}{n} (1-\eta)^{m-n} \ket{m}\bra{m},
\end{align}
for measurement outcome $n$, in the photon-number basis. And for non-number-resolved detection,
\begin{align}\index{Non-number-resolved photo-detectors}
&\hat\Pi_0 = \sum_{m=0}^\infty (1-\eta)^{m} \ket{m}\bra{m}, \nonumber \\
&\hat\Pi_{>0} = \mathbb{\hat{I}} - \hat\Pi_0.
\end{align}
Thus, inefficiency results in projection onto the wrong photon-number, making measurement outcomes incorrect.

@@

\subsubsection{Quantum non-demolition measurement (QND)}\index{Quantum non-demolition measurement (QND)}

@@

Quantum key distribution (QKD) is a relatively mature technology with already several commercial systems being available off-the-shelf \cite{??? example companies}. The main drawback is thus the ability to perform long-distance transmission of photons. For these reasons, current QKD networks have been limited to relatively small distances, on the order of $\sim100$km, including in Austria, Switzerland, Japan, USA, and China \cite{bib:lo2014secure}. The longest distance QKD network that is currently planned is the Beijing to Shanghai QKD link spanning a distance of 2000km. This involves 32 trusted nodes\index{Trusted nodes} to break the total distance into shorter segments to convert the quantum information to classical information.

Utilizing space communications for the purpose of QKD has been discussed in several works \cite{bib:hughes2000quantum, bib:rarity2002ground, bib:pfennigbauer2003free, bib:aspelmeyer2003long, bib:armengol08}. As already demonstrated in space-based entanglement experiments \cite{bib:yin2017satellite, bib:ren2017ground, bib:liao2017satellite} far lower attenuation rates are possible than ground-only approaches. Since cryptography schemes such as BB84\index{BB84 protocol} do not require entanglement, these would appear to be the first widespread commercial application for quantum technologies.

The ready realisability of space based QKD was already noted in a variety of configurations including ground-to-space\index{Ground-to-space communication} and space-to-ground\index{Space-to-ground communication} quantum communication \cite{bib:rarity2002ground, bib:aspelmeyer2003long}. In the context of security, the first long-distance experiments that are likely to be demonstrated will employ trusted nodes\index{Trusted nodes}. For example, after performing QKD between satellite\index{Satellites} and ground stations, a satellite could store the key for some time until another QKD can be performed to another ground station\index{Ground stations} using a one-time pad\index{One-time pad cipher} \cite{bib:liao2017satellite}. These types of experiments are planned to eventually perform intercontinental QKD\index{Intercontinental QKD} between China and Austria.

%
% One-Time Pad Cipher
%

\paragraph{One-time pad cipher}\index{One-time pad cipher}

@@

We now turn our attention to the technical implementation of QKD and its perfect security. There is only a single provably secure encryption protocol -- the \textit{one-time pad}\index{One-time pad cipher} \cite{bib:Schneier96}. This protocol requires Alice and Bob to share a random bit-string as long as the message (plaintext\index{Plaintext}) being communicated between them. The two bit-strings undergo bit-wise XOR operations to form the ciphertext\index{Ciphertext}. Mathematically,\index{One-time pad cipher}
\begin{align}
c = s \oplus k,
\end{align}
where $\oplus$ is the bitwise XOR operation (equivalently addition modulo 2), and $c$, $s$ and $k$ are the ciphertext, plaintext and key strings respectively, all of which are of the same length, \mbox{$|c|=|s|=|k|$}.

@@

Importantly, the secrecy of the one-time-pad\index{One-time pad cipher} strictly requires that a key never be reused. A fresh key must be generated for each message sent, otherwise trivial frequency analysis\index{Frequency analysis} techniques can be employed to compromise security\footnote{If the same key $k$ is used to encode two messages $s_1$ and $s_2$, yielding ciphertexts \mbox{$c_1=s_1\oplus k$} and \mbox{$c_2=s_2\oplus k$}, then we trivially obtain \mbox{$c_1 \oplus c_2 = s_1 \oplus k \oplus s_2 \oplus k = s_1 \oplus s_2$}. Now a frequency analysis on the bitwise XOR of two plaintexts can be applied, without requiring any knowledge of the key whatsoever.}.

Needless to say, the requirement for keys of the same length as the plaintexts, which cannot be reused, raises the obvious criticism that now secret key-sharing is as difficult as sharing a secret message in the first place. This reduces the problem of perfect secrecy of arbitrary messages to the secrecy of shared randomness. QKD protocols enable this by providing a shared source of randomness between Alice and Bob, where any intercept-resend attack\index{Intercept-resend attack} (or man-in-the-middle attack) may be detected, guaranteed by the laws of quantum physics (specifically the Heisenberg uncertainty principle\index{Heisenberg uncertainty principle} and no-cloning theorem\index{No-cloning theorem}).

@@

The two original QKD protocols, known as the \textit{BB84} \cite{bib:BennetBrassard84}\index{BB84 protocol}, and \textit{E91} \cite{bib:Ekert91}\index{E91 protocol} protocols, are based on polarisation encoding in photons. BB84 requires only the transmission of a sequence of single photons, polarisation-encoded\index{Polarisation encoding} with random data. E91, on the other hand, requires a server that distributes entangled Bell-pairs between Alice and Bob. Since then, numerous other protocols for QKD have been proposed, for example, using CV (ontinuous variable) states\index{Continuous variable QKD}.

Suppose an eavesdropper, Eve, were to perform an intercept-resend\index{Intercept-resend attack} attack on the channel between Alice and Bob. At that stage in the protocol Alice had not yet announced her choice of bases, and Eve will not know the bases in which to measure states without randomly collapsing them onto values inconsistent with Alice's encoding. By sacrificing a some of their shared bits, via openly communicating them to one another for comparison, such an attack will be detected with asymptotically high security. Thus, Alice and Bob have great confidence that they have a shared, secret, random bit-string, which may subsequently be employed in a one-time-pad.

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function BB84():
\begin{enumerate}
\item Alice chooses a random bit $0$ or $1$.
\item Alice randomly chooses a basis, $\hat{X}$ or $\hat{Z}$.
\item Depending on the choice of basis, she encodes her bit into the polarisation of a single photon as:
\begin{align}
\ket{0}_Z &\equiv \ket{H}, \nonumber \\
\ket{1}_Z &\equiv \ket{V},
\end{align}
or,
\begin{align}
\ket{0}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}+\ket{V}), \nonumber \\
\ket{1}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}-\ket{V}).
\end{align}
\item Encoding into the randomly chosen basis, she transmits the randomly chosen bit to Bob.
\item She does not announce the choice of bit or basis.
\item Bob measures the bit in a randomly chosen basis, $\hat{X}$ or $\hat{Z}$.
\item The above is repeated many times.
\item Upon receipt of all qubits, Alice (publicly) announces the basis used for encoding each bit sent.
\item Qubits where Bob measured in the opposite basis to which Alice encoded are discarded, as they will be decorrelated from Alice.
\item The remaining measurement outcomes are guaranteed to yield identical bits between Alice and Bob.
\item Remaining is roughly half as many bits as were sent, which are random, but guaranteed to be identical between Alice and Bob.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\end{enumerate}}}}
\caption{BB84 QKD protocol using polarisation-encoded\index{Polarisation encoding} photons. Upon completion of the protocol, Alice and Bob share a random bit-string.\index{One-time pad cipher}}\label{alg:bb84}
\end{table}

@@

Clock synchronization is a fundamental task with widespread applications, ranging from navigation, telecommunications, financial transactions, the internet, and many scientific applications. Of these, the Global positioning system (GPS)\index{Global positioning system (GPS)} has become a day-to-day necessity for much of humanity, having been increasingly incorporated into smartphones and other commodity devices.

The GPS system famously relies upon very precise clock synchronization to perform its task through a process of quadrangulation\index{Quadrangulation} from a constellation of several satellites. Due to the high speed of light, one requires in practice highly synchronized clocks which are accurate to a centralized time standard to the nanosecond level. This allows positioning to be performed to the level of meters, which is acceptable for many routine applications. GPS satellites have atomic clocks that are stable to one part in $10^{13}$, so that active correction can maintain accuracy to the nanosecond level. The great success of the GPS system in turn has created a further demand for increasingly precise navigation. For example, autonomous vehicles would immediately benefit from a more precise navigation system.

In principle, technology for more stable clocks already exists, with atomic clocks\index{Atomic clocks} exceeding stabilities of those on satellites being routinely produced, and optical atomic clocks now reaching stabilities of one part in $10^{18}$ \cite{bib:ludlow2015optical}. An outstanding question is then how to synchronize these clocks given their remarkable stabilities.

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{space_3}
\caption{Quantum clock synchronization schemes. (top) The proposal by Jozsa \& Dowling \textit{et al.} where a singlet state\index{Singlet state} is shared and measured in an ensemble of qubits \cite{bib:jozsa00}. (bottom) The proposal by Lukin \& Ye \textit{et al.} where a GHZ state\index{GHZ states} is distributed between satellites to measure the frequency drift at the Heisenberg limit \cite{bib:komar14}.}
\label{fig:space_3}
\end{figure}

Previous works have examined the problem of clock synchronization in space \comment{(see also Sec. [TB: refer to other section on clock sync])}. In the proposal of Jozsa \textit{et al.}, many copies of shared entanglement in a singlet state\index{Singlet state} is first distributed and stored on the clock states of an atomic clock \cite{bib:jozsa00}. The measurement is then performed by one party, which collapses the states simultaneously across all parties, and the time evolution of the states begins.

Classical information is exchanged between them, which reveals the time elapsed since the measurement, which can be used to synchronize the clocks. While the original protocol only allowed clock synchronization between two parties, similar ideas were used to extend this to the multiparty context \cite{bib:krvco2002quantum, bib:ben2011optimized, bib:ren2012clock}.

In a more recent proposal, a shared GHZ state\index{Greenberger-Horne-Zeilinger (GHZ) states} is prepared across all nodes in the quantum network, which allows for quantum metrologically enhanced detection\index{Quantum metrologically enhanced detection} of the clock signal drift at the Heisenberg limit\index{Heisenberg limit} \cite{bib:komar14}. The use of shared resources acts to improve the overall precision, allowing for an optimal scheme for the qubit resources that are employed. Several other proposals have also been made, which are quantum versions of Eddington's slow clock transport protocol\index{Eddington's slow clock transport protocol} where the qubit keeps time of the transmission \cite{bib:chuang2000quantum, bib:tavakoli2015quantum}.

Experimentally, there have been several demonstrations of the protocol, albeit at relatively short distances. Continuous time-bin\index{Time-bin encoding} entangled photons were used as the entanglement resource to obtain a time-correlation between a distance of 3km \cite{bib:valencia2004distant}, and another technique based on Hong-Ou-Mandel interferometry\index{Hong-Ou-Mandel interferometry} was performed across a 4km fiber link \cite{bib:quan2016demonstration}. Several other demonstrations based on nuclear magnetic resonance (NMR)\index{Nuclear magnetic resonance} \cite{bib:zhang2004nuclear, bib:kong2017implementation} have also been performed.

There are however several outstanding problems with the quantum clock synchronization scheme as presented above. In the scheme of Jozsa \textit{et al.}, if one starts in a perfect singlet state\index{Singlet state}, the scheme works as intended, but if one instead starts with the state, 
\begin{align}
\frac{1}{\sqrt{2}} ( | 0 \rangle_A | 1 \rangle_B - e^{i \delta} | 1 \rangle_A | 0 \rangle_B ),
\end{align}
(a Bell pair augmented by a local phase) one obtains an offset to the synchronizations between the two parties. In practice, such a phase could arise from decoherence induced noise, or differences in the basis conventions chosen by the two parties. Thus, in practice entanglement purification\index{Entanglement purification} would be required to produce a singlet state with \mbox{$\delta=0$} prior to executing the protocol. However, it was argued that to perform the entanglement purification quantum circuit correctly, the timing of the quantum gates would need to be controlled, which requires synchronized clocks \cite{bib:preskill2000quantum} --  this renders syncrhonization impossible. It has previously been shown that such a phase cannot be eliminated using asynchronous entanglement purification\index{Entanglement purification} \cite{bib:yurtsever02}, and hence the protocol remains incomplete in the general case where imperfect singlet pairs\index{Singlet state} are shared.

### 2017-09-22 Sections/quantum_channels.tex
indexing

Quantum processes are most easily represented using \textit{Kraus operators}, $\{\hat{K}_i\}$,
\begin{align} \label{eq:kraus_rep}
\mathcal{E}(\hat\rho) = \sum_i \hat{K}_i \hat\rho \hat{K}_i^\dag,
\end{align}
where,
\begin{align}
\sum_i \hat{K}_i^\dag \hat{K}_i = \hat{\mathbb{I}},
\end{align}
for normalisation. Here $\mathcal{E}$ is a super-operator, denoting the action of the process on state $\hat\rho$. This is also referred to as the \textit{operator-sum representation}\index{Operator-sum representation}. This representation has the elegant interpretation as the probabilistic application of each of the Kraus operators $\hat{K}_i$, with probability,
\begin{align}
p_i = \text{tr}(\hat{K}_i \hat\rho \hat{K}_i^\dag).
\end{align}
In the ideal case, the two types of evolution of interest are unitary evolution, in which case there is only one Kraus operator, \mbox{$\hat{K}_1=\hat{U}$}, and projective measurement, where there is again only one Kraus operator, \mbox{$\hat{K}_1=\ket{m}\bra{m}$}, for measurement outcome $m$.

@@

In general, the Kraus operator representation for quantum processes is not unique -- there may be multiple choices of Kraus operators that implement identical processes. But if the representation is not unique, how do we compare different quantum processes? To address this, it is common to choose a `standard' basis for representing quantum processes, such that they may be consistently and fairly compared. This requires choosing a basis which is complete for operations on the Hilbert space acted upon by the process.

For example, for a single qubit, the Pauli operators -- $\hat\sigma_1$ (identity, $\mathbb{\hat{I}}$), $\hat\sigma_2$ (bit-flip, $\hat{X}$), $\hat\sigma_3$ (bit-phase-flip, $\hat{Y}$), and $\hat\sigma_4$ (phase-flip, $\hat{Z}$) -- are complete for single-qubit operations ($\mathbb{C}_2$). Therefore by decomposing our Kraus operators into linear combinations of these basis operators we have a standardised representation for single-qubit processes. Formally, for one qubit,
\begin{align} \label{eq:process_matrix}
\mathcal{E}(\hat\rho) = \sum_{i,j=1}^4 \chi_{i,j} \hat{\sigma}_i\hat\rho\,\hat{\sigma}_j^\dag.
\end{align}

The Hermitian matrix $\chi$ is known as the \textit{process matrix}, from which many other metrics of interest may be directly computed (some of which are discussed in Sec.~\ref{sec:quantum_meas_cost}). Process matrices share many properties and interpretations in common with density matrices. The diagonal elements can be regarded as the amplitudes associated with applying each of the four Pauli operators, all of which are non-negative, while the off-diagonal elements represent the coherences between them, i.e whether the operations on the diagonal are being applied probabilistically or coherently. For the process to be trace preserving we require,
\begin{align}
\text{tr}(\chi) = 1.
\end{align}

>>>>

Quantum processes are most easily represented using \textit{Kraus operators}\index{Kraus operators}, $\{\hat{K}_i\}$,
\begin{align} \label{eq:kraus_rep}
\mathcal{E}(\hat\rho) = \sum_i \hat{K}_i \hat\rho \hat{K}_i^\dag,
\end{align}
where,
\begin{align}
\sum_i \hat{K}_i^\dag \hat{K}_i = \hat{\mathbb{I}},
\end{align}
for normalisation. Here $\mathcal{E}$ is a super-operator, denoting the action of the process on state $\hat\rho$. This is also referred to as the \textit{operator-sum representation}\index{Operator-sum representation}. This representation has the elegant interpretation as the probabilistic application of each of the Kraus operators $\hat{K}_i$, with probability,
\begin{align}
p_i = \text{tr}(\hat{K}_i \hat\rho \hat{K}_i^\dag).
\end{align}
In the ideal case, the two types of evolution of interest are unitary evolution, in which case there is only one Kraus operator, \mbox{$\hat{K}_1=\hat{U}$}, and projective measurement, where there is again only one Kraus operator, \mbox{$\hat{K}_1=\ket{m}\bra{m}$}, for measurement outcome $m$.

@@

In general, the Kraus operator representation for quantum processes is not unique -- there may be multiple choices of Kraus operators that implement identical physical processes. But if the representation is not unique, how do we compare different quantum processes? To address this, it is common to choose a `standard' basis for representing quantum processes, such that they may be consistently and fairly compared. This requires choosing a basis which is complete for operations on the Hilbert space acted upon by the process.

For example, for a single qubit, the Pauli operators\index{Pauli operators} -- $\hat\sigma_1$ (identity, $\mathbb{\hat{I}}$), $\hat\sigma_2$ (bit-flip, $\hat{X}$), $\hat\sigma_3$ (bit-phase-flip, $\hat{Y}$), and $\hat\sigma_4$ (phase-flip, $\hat{Z}$) -- are complete for single-qubit operations ($\mathbb{C}_2$). Therefore by decomposing our Kraus operators into linear combinations of these basis operators we have a standardised representation for single-qubit processes. Formally, for one qubit,
\begin{align} \label{eq:process_matrix}
\mathcal{E}(\hat\rho) = \sum_{i,j=1}^4 \chi_{i,j} \hat{\sigma}_i\hat\rho\,\hat{\sigma}_j^\dag.
\end{align}

The Hermitian matrix $\chi$ is known as the \textit{process matrix}\index{Process matrix}, from which many other metrics of interest may be directly computed (some of which are discussed in Sec.~\ref{sec:quantum_meas_cost}).

Process matrices share many algebraic properties and interpretations in common with density matrices. The diagonal elements can be regarded as the amplitudes associated with applying each of the four Pauli operators, all of which are non-negative, while the off-diagonal elements represent the coherences between them, i.e whether the operations on the diagonal are being applied probabilistically or coherently. For example, a process that simply randomly applies Pauli operators would have a diagonal process matrix in the Pauli basis. But off-diagonal elements would be indicative of applying coherent superpositions of the operators.

For the process to be trace preserving we require,
\begin{align}
\text{tr}(\chi) = 1.
\end{align}
We will typically enforce this constraint on our processes. $\text{tr}(\chi) < 1$ implies non-determinism, i.e the process sometimes fails.
